Recruiting Chapter

### 2021-06-16 text/tables_figures_june_2021.Rmd
add 1-mode matrix tables by cluster for public + private universities

kable(table_1mode_privc$onemode_pct_df, caption = 'Private colleges percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(1, width = '8.5em') %>%
  column_spec(2:13, width = '7em') %>% 
  column_spec(11, width = '6em')
```

>>>>

kable(table_1mode_privc$onemode_pct_df, caption = 'Private colleges percent matrix') %>%
  kable_styling(latex_options = 'scale_down') %>%
  column_spec(1, width = '8.5em') %>%
  column_spec(2:13, width = '7em') %>% 
  column_spec(11, width = '6em')

table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))

kable(table_1mode_u$clusters_df[order(match(table_1mode_u$clusters_df$univ_abbrev, rownames(table_1mode_u$onemode_df))), ], caption = 'Clusters for public and private universities')

cluster_1 <- c(13, 17, 21, 26, 27)
cluster_2 <- c(2, 3, 6, 8, 9, 10, 11, 12, 14, 15, 20, 22, 23)
cluster_3 <- c(1, 4, 5, 7, 16, 18, 19, 24, 25, 28)
cluster_4 <- 29

kable(table_1mode_u$onemode_df[cluster_1, cluster_1], caption = 'Public and private universities count matrix (cluster 1)') %>%
  kable_styling(latex_options = 'scale_down')

kable(table_1mode_u$onemode_pct_df[cluster_1, cluster_1], caption = 'Public and private universities percent matrix (cluster 1)') %>%
  kable_styling(latex_options = 'scale_down')

kable(table_1mode_u$onemode_df[cluster_2, cluster_2], caption = 'Public and private universities count matrix (cluster 2)') %>%
  kable_styling(latex_options = 'scale_down')

kable(table_1mode_u$onemode_pct_df[cluster_2, cluster_2], caption = 'Public and private universities percent matrix (cluster 2)') %>%
  kable_styling(latex_options = 'scale_down')

kable(table_1mode_u$onemode_df[cluster_3, cluster_3], caption = 'Public and private universities count matrix (cluster 3)') %>%
  kable_styling(latex_options = 'scale_down')

kable(table_1mode_u$onemode_pct_df[cluster_3, cluster_3], caption = 'Public and private universities percent matrix (cluster 3)') %>%
  kable_styling(latex_options = 'scale_down')

```
